Performance of two different ontological and data access methods

### 2014-07-03 cold2014/magnus.tex
change the formulation of external validity a bit
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@716 43ef1190-90fd-4dd7-a769-d0121f02b80e

Since the present study represents a common use case for Semantic Web
application, we are of the opinion that there is a strong case for its
external validity, but it does obviously rely on that the study itself
is valid.

>>>>

Since the present study uses actually deployed ontologies and data,
and also addresses a common use case for Semantic Web applications, we
are of the opinion that there is a strong case for its external
validity, but it does obviously rely on that the study itself is
valid.
